Final Ratings for Genome Biology

### 2018-10-26 manuscript_figures/manuscript_ratings.Rmd
Change legend title in ratings figure

```{r, fig.width = 10, fig.height = 8}
p1a <- bind_rows(Yeast = fdrcontrol_yeast, Sims = fdrcontrol_sims, .id = "Analysis") %>%
    dplyr::mutate(Method = reorder(Method, pExceeds),
                  Analysis = factor(Analysis, levels = c("Yeast", "Sims"))) %>%
    ggplot(aes(x = Method, y = pExceeds, color = Method, group = Analysis)) +
    geom_line(aes(linetype = Analysis), color = 'black', alpha = 1/2) +
    geom_point(size = 3) + 
    scale_color_manual(values = col, guide = FALSE) +
    scale_x_discrete(NULL) + 
    scale_y_continuous("% settings exceeding nominal FDR", labels = scales::percent) + 
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("FDR Control")

p1b <- bind_rows(Yeast = power_yeast, Sims = power_sims, .id = "Analysis") %>%
    dplyr::mutate(Method = reorder(Method, meanRank),
                  Analysis = factor(Analysis, levels = c("Yeast", "Sims"))) %>%
    ggplot(aes(x = Method, y = meanRank, color = Method, group = Analysis)) +
    geom_line(aes(linetype = Analysis), color = 'black', alpha = 1/2) +
    geom_point(size = 3) + 
    scale_color_manual(values = col, guide = FALSE) +
    scale_x_discrete(NULL) + 
    scale_y_continuous("Mean TPR rank", breaks = 0:10) + 
    expand_limits(y = 1) +
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("Power")

p1c <- bind_rows(Sims = consistency2_sims, CS = consistency2_data, .id = "Analysis") %>%
    dplyr::mutate(Method = reorder(Method, propEither95),
                  Analysis = factor(paste0(Analysis, " (", key, ")")),
                  Aanlysis = factor(Analysis, levels = levels(Analysis)[c(2, 3, 1)])) %>%
    ggplot(aes(x = Method, y = propEither95, color = Method, group = Analysis)) +
    geom_line(aes(linetype = Analysis), color = 'black', alpha = 1/2) +
    geom_point(size = 3) + 
    scale_color_manual(values = col, guide = FALSE) +
    scale_x_discrete(NULL) + 
    scale_y_continuous("% settings w/ metric\n < 95% of BH and q-value", labels = scales::percent) + 
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("Consistency (I)")

p1d <- bind_rows(Sims = consistency_sims, CS = consistency_data, .id = "Analysis") %>%
    dplyr::mutate(Method = reorder(Method, sdRGain),
                  Analysis = factor(paste0(Analysis, " (", key, ")"))) %>%
    ggplot(aes(x = Method, y = sdRGain, color = Method, group = Analysis)) +
    geom_line(aes(linetype = Analysis), color = 'black', alpha = 1/2) +
    geom_point(size = 3) + 
    scale_color_manual(values = col, guide = FALSE) +
    scale_x_discrete(NULL) + 
    scale_y_continuous("SD of log-ratio relative to\nmean of BH and q-value") + 
    expand_limits(y = 1) +
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("Consistency (II)")

@@

>>>>

```{r, fig.width = 10, fig.height = 8}
p1a <- bind_rows(Yeast = fdrcontrol_yeast, Sims = fdrcontrol_sims, .id = "Study") %>%
    dplyr::mutate(Method = reorder(Method, pExceeds),
                  Study = factor(Study, levels = c("Yeast", "Sims"))) %>%
    ggplot(aes(x = Method, y = pExceeds, color = Method, group = Study)) +
    geom_line(aes(linetype = Study), color = 'black', alpha = 1/2) +
    geom_point(size = 3) + 
    scale_color_manual(values = col, guide = FALSE) +
    scale_x_discrete(NULL) + 
    scale_y_continuous("% settings exceeding nominal FDR", labels = scales::percent) + 
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("FDR Control")

p1b <- bind_rows(Yeast = power_yeast, Sims = power_sims, .id = "Study") %>%
    dplyr::mutate(Method = reorder(Method, meanRank),
                  Study = factor(Study, levels = c("Yeast", "Sims"))) %>%
    ggplot(aes(x = Method, y = meanRank, color = Method, group = Study)) +
    geom_line(aes(linetype = Study), color = 'black', alpha = 1/2) +
    geom_point(size = 3) + 
    scale_color_manual(values = col, guide = FALSE) +
    scale_x_discrete(NULL) + 
    scale_y_continuous("Mean TPR rank", breaks = 0:10) + 
    expand_limits(y = 1) +
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("Power")

p1c <- bind_rows(Sims = consistency2_sims, CS = consistency2_data, .id = "Metric") %>%
    dplyr::mutate(Method = reorder(Method, propEither),
                  Metric = factor(paste0(Metric, " (", key, ")"))) %>%
    ggplot(aes(x = Method, y = propEither, color = Method, group = Metric)) +
    geom_line(aes(linetype = Metric), color = 'black', alpha = 1/2) +
    geom_point(size = 3) + 
    scale_color_manual(values = col, guide = FALSE) +
    scale_x_discrete(NULL) + 
    scale_y_continuous("% settings w/ metric < classic methods", labels = scales::percent) + 
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("Consistency of Gain")

p1d <- bind_rows(Sims = consistency_sims, CS = consistency_data, .id = "Metric") %>%
    dplyr::mutate(Method = reorder(Method, sdRGain),
                  Metric = factor(paste0(Metric, " (", key, ")")),
                  Metric = factor(Metric, levels = levels(Metric)[c(1, 3, 2)])) %>%
    ggplot(aes(x = Method, y = sdRGain, color = Method, group = Metric)) +
    geom_line(aes(linetype = Metric), color = 'black', alpha = 1/2) +
    geom_point(size = 3) + 
    scale_color_manual(values = col, guide = FALSE) +
    scale_x_discrete(NULL) + 
    scale_y_continuous("SD of log-ratio relative to classic methods") + 
    expand_limits(y = 1) +
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("Relative Consistency")

@@

Additionally, we consider creating the above plot with a common x-axis.

```{r, fig.width = 10, fig.height = 8}
consistency_order <- c("bh", "qvalue", "bl", "ihw", "lfdr", "fdrreg-t", "ashq", "adapt-glm")

p2a <- bind_rows(Yeast = fdrcontrol_yeast, Sims = fdrcontrol_sims, .id = "Study") %>%
    dplyr::mutate(Method = reorder(Method, pExceeds),
                  Study = factor(Study, levels = c("Yeast", "Sims"))) %>%
    ggplot(aes(x = Method, y = pExceeds, color = Study, group = Study)) +
    geom_point(size = 3, position = position_dodge(width = 1/4)) + 
    scale_color_brewer(palette = "Set2") + 
    scale_x_discrete(NULL, limits = consistency_order) + 
    scale_y_continuous("% settings exceeding nominal FDR", labels = scales::percent) + 
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("FDR Control")

p2b <- bind_rows(Yeast = power_yeast, Sims = power_sims, .id = "Study") %>%
    dplyr::mutate(Method = reorder(Method, meanRank),
                  Study = factor(Study, levels = c("Yeast", "Sims"))) %>%
    ggplot(aes(x = Method, y = meanRank, color = Study, group = Study)) +
    geom_point(size = 3, position = position_dodge(width = 1/4)) + 
    scale_color_brewer(palette = "Set2") + 
    scale_x_discrete(NULL, limits = consistency_order) + 
    scale_y_continuous("Mean TPR rank", breaks = 0:10) + 
    expand_limits(y = 1) +
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("Power")

p2c <- bind_rows(Sims = consistency2_sims, CS = consistency2_data, .id = "Metric") %>%
    dplyr::mutate(Method = reorder(Method, propEither),
                  Metric = factor(paste0(Metric, " (", key, ")"))) %>%
    ggplot(aes(x = Method, y = propEither, color = Metric, group = Metric)) +
    geom_point(size = 3, position = position_dodge(width = 1/4)) +
    scale_color_brewer(palette = "Set1") + 
    scale_x_discrete(NULL, limits = consistency_order) + 
    scale_y_continuous("% settings w/ metric < classic methods", labels = scales::percent) + 
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("Consistency of Gain")

p2d <- bind_rows(Sims = consistency_sims, CS = consistency_data, .id = "Metric") %>%
    dplyr::mutate(Method = reorder(Method, sdRGain),
                  Metric = factor(paste0(Metric, " (", key, ")")),
                  Metric = factor(Metric, levels = levels(Metric)[c(1, 3, 2)])) %>%
    ggplot(aes(x = Method, y = sdRGain, color = Metric, group = Metric)) +
    geom_point(size = 3, position = position_dodge(width = 1/4)) + 
    scale_color_brewer(palette = "Set1") + 
    scale_x_discrete(NULL, limits = consistency_order) + 
    scale_y_continuous("SD of log-ratio relative to classic methods") + 
    expand_limits(y = 1) +
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    ggtitle("Relative Consistency")

p2title <- ggdraw() +
    draw_label("Summary Recommendation Metrics",
               fontface = 'bold')

p2ab <- plot_grid(p2a + guides(color = FALSE),
                  p2b + guides(color = FALSE),
                  labels = LETTERS[1:2], nrow = 1)
p2ab <- plot_grid(p2ab, get_legend(p2a), nrow = 1, rel_widths = c(1, .2))

p2cd <- plot_grid(p2c + guides(color = FALSE),
                  p2d + guides(color = FALSE),
                  labels = LETTERS[3:4], nrow = 1)
p2cd <- plot_grid(p2cd, get_legend(p2d), nrow = 1, rel_widths = c(1, .2))

FigS2 <- plot_grid(p2title, p2ab, p2cd, ncol = 1, rel_heights = c(.2, 1, 1))
FigS2

ggsave(file.path(outdir, "SFigureMetrics-fixedorder.pdf"), width=10, height=8)
```
